Explain urban regional function

### 2018-11-22 paper.tex
1122

\section{Introduction}
%urban computing
Urban computing, defined in~\cite{Zheng2014UrbanConcepts} as a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces.%definition
One of the most important data source is human mobility data, e.g. pick-ups and drop-offs of taxicabs.
Such mobility data can contribute to improve living quality of residents, e.g. optimizing urban planning~\cite{Zheng2011taxicabs}, easing traffic congestion~\cite{Meng2017Traffic}, decreasing energy consumption ~\cite{Zhang2015Fuel}, reducing air pollution~\cite{Shang2014Pollution} and so on.
Therefore, mining and modeling mobility data has attracted attentions from both academia and industry.

%region function
Identifying functional regions has been a critical step towards efficient government administration and policy making for decades.
In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
Later work focuses on city-level functional region identification, where a functional region is a region in a city which supports different needs of people’s urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.
To obtain accurate identification, recent research tends to use complex models for various form of data,
e.g. latent factor models based on Dirichlet Multinomial Regression are applied on mobility data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}, clustering algorithm based on the 'modularity function' is applied on telecommunication~\cite{Newman2004ModularityFunction,Ratti2010Telecom},unsupervised semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}. %complex model

\textbf{Motivation.}
%explainability
A severe drawback of existing research is the lack of explanation for the identifications of functional regions. Though existing applications~\cite{Yuan2015FunctionRegion} have achieved high identification accuracy,the complex nature of these models weakens the interpretability to end users and system designers.%The lack of explanation of the identification xxx
There is an emerging trend in studying explainable AI~\cite{Preece2018ExplainAI}.
In geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.
To the best of our knowledge, none of the previous urban functional identification provide explanation for the results of region segmentation and functional labels.

@@

As shown in Fig.\ref{explanation-example}, our system not only segments regions of a city based on the functionals, but also delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

@@

%extract the different among these data
The simplest form of mobility data is \textbf{check-ins data}, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
Statistical association analysis is commonly conducted on check-ins. For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers’ refueling decision~\cite{Zhang2015Fuel}.

@@

@@

Recently, an emerging research interest is witnessed in exploring the geographical factors that affect online sentiment.
Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{González2008Track},to find the geographical content analysis with sentiment.
Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{Alshamsi15milan},a high check-in density region usually presents a more positive mode~\cite{Gallegos16happier}, the whole process and development of a organized movement could be tracked on the social media~\cite{Alvarez2015Movement} and so on.

@@

\begin{thebibliography}{25}
\bibitem{Zheng2014UrbanConcepts}Zheng Y, Capra L, Wolfson O, et al. Urban Computing:Concepts, Methodologies, and Applications[J]. Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.
    %综述城市计算的概念和框架
\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.
    %利用GPS轨迹检测出现有城市规划中存在的缺陷。结果包括：1）存在显著交通问题的区域对，2）连接结构以及它们之间的相关性。这些结果可以评估所实施的规划的有效性，例如一个城市新建的公路和地铁线路，并提醒城市规划者在构思未来规划时没有认识到的问题。
\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y. City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories. Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10
    %提出了一个框架来推断城市交通流量信息与环路探测器和出租车轨迹。

\bibitem{Vatsavai2011Remote}Vatsavai R R, Bright E, Varun C, et al. Machine learning approaches for high-resolution urban land cover classification:a comparative study[C]// International Conference and Exhibition on Computing for Geospatial Research \& Application, Com.geo 2011, Washington, Dc, Usa, May. DBLP, 2011:1-10.
    %利用遥感数据生成主题地图
\bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S. Unsupervised Semantic Labeling Framework for Identification of Complex Facilities in High-Resolution Remote Sensing Images[C]// IEEE International Conference on Data Mining Workshops. IEEE Computer Society, 2010:273-280.
    %利用遥感数据生成主题地图

@@

    %利用电信数据库来划分地图。
\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al. A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August. DBLP, 2011:735-738.
    %利用轨迹点来提升司机收入
\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp
    %对之前的functional region做了一个总结。
\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu. Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!. In KDD ’18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19–23, 2018, London, United Kingdom. 2018.
    %通过Minimizing Distance through Monte Carlo Tree Search来对出租车司机进行路线推荐，使其提高效率，降低空载率。

@@

    %最早提出用出租车轨迹来做功能区划分。但是早期数据都来自司机填写调查问卷，不够准确且数据较小，因此研究的东西比较初步，只能表明伦敦中心区包含许多具有强大内部联系的非常独立的功能区。

@@

    %对现有（2006）的功能区识别方法做了总结，将方法归纳为三类：
    %（1）基于不同城市核心区之间通勤频率的比较的当地劳动力市场方法
    %（2）通勤区方法（Killian等。1993年，它建立在现有的城市相互依存的基础上，并衡量地区之间双向通勤联系的强度
    %(3)无障碍方法，它利用两种无障碍方式：雇主与工人的接触。获得工作机会。

@@

    %模块化方法的鼻祖
\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
    %早期的Urban function定义
\bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X. Discovering regions of different functions in a city using human mobility and POIs[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. ACM, 2012:186-194.
    %套用LDA，根据功能划分城市区域

@@

    %引入latent activity，对他自己2012的论文做了一个拓展，提高精确度

@@

    %对之前functional region工作的一个总结，没有再加入新的提高

@@

    %提出了一个智能系统，用于利用出租车轨迹、POI、道路网络和在线用户的报告来发现城市加油行为。

@@

    %本文利用车辆轨迹（例如出租车）的GPS轨迹，即时推断出在城市时速路段上行驶的车辆的气体消耗量和污染排放量。

@@

    %寻找时空可达区域
    %

@@

    %用深度神经网络来预测旅行时间
    %
\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1–13, 2015
    %从社交网站上挖掘15M这个运动的组织、形成与爆发
    %

@@

    %把米兰城区划分成100*100区域，根据社交网络发现情绪积极的region更喜欢和其他积极的region交流。

@@

    %check-in数据来自整个美国.         用户有周期性的行为模式（weekly），受地理、经济、个人社会地位（粉丝越多地位越高）约束，需要content来更好地理解.引入回转半径来帮助sentiment（实际文本分析还是靠字典）
\bibitem{González2008Track}González M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.
    %追踪100000名手机用户6个月，人体轨迹表现出高度的时间和空间规律。说是human mobility, 但是数据集是长期轨迹包含很多点

@@

    %将其他人的统计方法用于划分区域的签到数据集中，比较得出结论：① 签到数据越多的地方积极性越高，消极性越低。②发现在签到数据多的地方签到的用户，活动范围都比较大。可以理解为这个地方比较吸引人，人们愿意走更远的路去这里玩。③结合人口普查的结果，发现签到数据多的地方所居住的居民年龄更大、非西班牙裔人口更多、受教育程度更高

@@

    %对截止16年最新的50篇与LSBN和POI相关的顶会论文做了一个总结，不知道能不能用上
\bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang. SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018). In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR ’18). 2018.
    %概述了推荐系统中explanation的重要性

@@

    %介绍了推荐系统解释的调查概述和未来新视角。主要看了explanation的几种形式
    %基于内容、特征的explanation：利用用户a感兴趣的特征和商品b所拥有的特征来匹配。用户对推荐系统的满意度和信任度与解释高度相关。形式有雷达图等。
    %基于文本的句子形式explanation：在评论等数据中获得更加完善的用户倾向，生成文本句子作为解释。情感抽取工具Sentires（toolkit是一个jre，已得到，未运行），可抽取feature-Opinion-sentiment三元组

@@

    %为了证明explanation facilities 能提高推荐系统的acceptance，本文通过对210个MovieLens用户的调查，发现绝大部分用户希望在推荐结果中加入explanation。
    %

@@

    %这篇只发表在作者自己的网站上，但是有被引用。内容是选择过多时，用户满意度会下降。这篇文章通过实验证明，用户的满意度和解释性有关。
    %
\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
    Zhang Y, Lai G, Zhang M, et al. Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval. ACM, 2014:83-92.
    %开发了一个情感抽取工具Sentires，在短语这个级别层面上做情感极性标注。可以从某个产品领域的产品评论中抽取“feature-oppion-sentiment”这样的三元组。例如，在手机领域，“noise-high-negative”，“screen-clear-positive”等。
    %对于我们的大众点评数据，也可以“feature-opinion-sentiment”。其中feature表示52个标签，opinion表示评分，sentiment表示根据评分是积极or消极（与feature其实无关）
\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017.
    %提出了一个LSTM模型来生成评论。并提出八个评估生成文字可读性的测量标准
\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63–72.
    %explain AI
\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator. In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems. In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al. Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April. DBLP, 2011:347-356.
\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S . Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems. ACM, 2017.
\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
\end{thebibliography}
\end{document}

>>>>

\section{Introduction}
%urban computing
Urban computing is a process of acquisition, integration and analysis of big and heterogeneous data generated by diverse sources in urban spaces~\cite{Zheng2014UrbanConcepts}. 
Recently, urban computing has attracted attentions from both academy and industry.
One critical step towards efficient urban computing is to identify functional regions, which is a region in a city that supports certain needs of urban lives~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%related work survey
Most of previous functional region identification systems use clustering methods on mobility data~\cite{Karlsson2006FunctionalRegionSummary}. such as origin-destination pairs of labour market data~\cite{Karlsson2006FunctionalRegionSummary}.
For example, clustering algorithm based on the 'modularity function' is applied on telecommunication data~\cite{Newman2004ModularityFunction,Ratti2010Telecom}, semantic labeling framework based on the Latent Dirichlet Allocation is applied on remote-sensor data~\cite{Vatsavai2010Remote}, spectural clustering is applied on remote-sensor image data~\cite{Vatsavai2011Remote}, and DMR (Dirichlet Multinomial Regression) are applied on pick-ups and drop-offs data of taxicabs and points of interests (POIs)~\cite{Yuan2012FunctionRegion,Yuan2015FunctionRegion}.

%problem of past research
A severe drawback of existing research is the lack of explanation for functional regions.
Clustering methods have long been suffering from the subjective issue, i.e. the system only provides one possible partitioning of the regions while the users have no idea what the partitioning means. 
Furthermore, to obtain accurate identification, recent research tends to use complex models~\cite{Yuan2015FunctionRegion} on a combination of different data sources. 
The complex nature of these models is an obstacle for people to capture the ``semantics'' of the identification.

%motivation
Explainable functional region identification is beneficial for both system designers and end users.
For example, providing explanations help system designers to better intepretate the clustering results and improve the system. 
The explanations can incubate a series of applications for end users, including traffic flow predictions, personalized trajectory recommendation, urban planning and so on. 
In a bigger picture, there is a growing interest in studying explainable AI~\cite{Preece2018ExplainAI}.
However, in geographical systems, explainable system is still in its initial stage~\cite{Korpan2017navigation,Jose2018cognitive}.

%goal
In this paper, we present a novel system for explainable functional region identification. The system provides post-hoc explanations, i.e. the explanations are not relevant to the identification algorithm. Instead, the system attempts to resolve the ``semantics" of cluster labels generated by any functional region identification algorithm by (1) associating the cluster labels to a set of human activities; (2) visualizing the desired urban features and public sentiments for each activity; and (3) listing the most important urban features in the region.

As shown in Fig.\ref{explanation-example}, the city of Chengdu has been functional regions delivers explanations of the  functionals. To be specific, we first associate each functional with an urban activity, next we extract the most representative urban feature for each activity, finally we highlight the sentiment towards typical urban features for each functional region.  For example,Fig.\ref{explanation-example} given a map of city A, reg region I corresponds to residential region while blue region II corresponds to commercial region. We found that people are most interested on traffic for a commercial region. And a residential region usually has sentiment positive on vanishing noise.

@@

@@

%extract the different among these data
The simplest form of mobility data is \textbf{check-ins data}, which are collected from locating sharing services. Check-ins data usually includes a set of point revealing users' current location.
Statistical association analysis is commonly conducted on check-ins. For example, radius of gyration is measured in~\cite{Cheng2011Check-in}, which is extended by combining with lexicon into demographics~\cite{Gallegos16happier}.
A few recent work adopts model based approaches, e.g. context-aware tensor factorization that take account of contextual factors that influence consumers refueling decision~\cite{Zhang2015Fuel}.

@@

In early work, a functional region was defined as a geographical region where the majority of local population recruit and are employed within the region \cite{Ball1980Definition}.
Due to the availability of large-scale mobility data, an increasing amount of data-driven approaches~\cite{Farmer2009Overview} have been proposed.
Most of them use clustering methods on commuting data, such as origin-destination pairs of labour market data ~\cite{Karlsson2006FunctionalRegionSummary} while others use remote-sensor image data~\cite{Vatsavai2011Remote}.
Later work focuses on city-level functional region identification,

@@

Recently, an emerging research interest is witnessed in exploring the geographical factors that affect online sentiment.
Empirical studies have been conducted on large-scale human mobility data, such as check-in ~\cite{Gallegos16happier}and trajectory~\cite{Gonzlez2008Track},to find the geographical content analysis with sentiment.
Associations are found between online sentiments and geographical factors, e.g happy regions are more likely to connect with each other~\cite{Alshamsi15milan},a high check-in density region usually presents a more positive mode~\cite{Gallegos16happier}, the whole process and development of a organized movement could be tracked on the social media~\cite{Alvarez2015Movement} and so on.

@@

\begin{thebibliography}{25}
\bibitem{Zheng2014UrbanConcepts}Zheng Y, Capra L, Wolfson O, et al. Urban Computing:Concepts, Methodologies, and Applications[J]. Acm Transactions on Intelligent Systems \& Technology, 2014, 5(3):1-55.

\bibitem{Zheng2011taxicabs}Zheng Y, Liu Y, Yuan J, et al. Urban computing with taxicabs[C]// International Conference on Ubiquitous Computing. ACM, 2011:89-98.

\bibitem{Meng2017Traffic}Meng, C.; Yi, X.; Su, L.; Gao, J.; Zheng, Y. City-wide Traffic Volume Inference with Loop Detector Data and Taxi Trajectories. Proceedings of the 25th ACM SIGSPATIAL International Conference on Advances in Geographic Information Systems,ACM,2017, 1:1-1:10

\bibitem{Vatsavai2011Remote}Vatsavai R R, Bright E, Varun C, et al. Machine learning approaches for high-resolution urban land cover classification:a comparative study[C]// International Conference and Exhibition on Computing for Geospatial Research \& Application, Com.geo 2011, Washington, Dc, Usa, May. DBLP, 2011:1-10.

\bibitem{Vatsavai2010Remote}Vatsavai R R, Cheriyadat A, Gleason S. Unsupervised Semantic Labeling Framework for Identification of Complex Facilities in High-Resolution Remote Sensing Images[C]// IEEE International Conference on Data Mining Workshops. IEEE Computer Society, 2010:273-280.

@@

\bibitem{Yuan2010NextPassenger}Yuan J, Zheng Y, Zhang L, et al. Where to find my next passenger[C]// Proceedings of the 13th international conference on Ubiquitous computing. ACM, 2011:109-118.
\bibitem{Ge2011TaxiBusiness}Ge Y, Liu C, Xiong H, et al. A taxi business intelligence system[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining, San Diego, Ca, Usa, August. DBLP, 2011:735-738.
\bibitem{Farmer2009Overview}Farmer, C. J. (2009). Data driven functional regions. In Proceedings of 10th International Conference on GeoComp

\bibitem{Garg2018Route}Nandani Garg and Sayan Ranu. Route Recommendations for Idle Taxi Drivers: Find Me the Shortest Route to a Customer!. In KDD 18: The 24th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining, August 19-23, 2018, London, United Kingdom. 2018.

@@

@@

@@

\bibitem{Ball1980Definition}R.M. Ball. The use and definition of Travel-to-Work Areas in Great Britain: Some problems[J]. Regional Studies, 1980, 14(2):125-139.
\bibitem{Yuan2012FunctionRegion}Yuan J, Zheng Y, Xie X. Discovering regions of different functions in a city using human mobility and POIs[C]// ACM SIGKDD International Conference on Knowledge Discovery and Data Mining. ACM, 2012:186-194.

@@

@@

@@

@@

@@

@@

\bibitem{Alvarez2015Movement}R. Alvarez, D. Garcia, Y. Moreno, and F. Schweitzer. Sentiment cascades in the 15m movement. EPJ Data Science, 4(1):1-13, 2015

@@

@@

\bibitem{Gonzlez2008Track}Gonzlez M C, Hidalgo C A. Understanding individual human mobility patterns[J]. Nature, 2008, 453(7196):779-782.

@@

@@

\bibitem{Zhang2018SIGIR}Yongfeng Zhang, Yi Zhang, and Min Zhang. SIGIR 2018 Workshop on ExplainAble Recommendation and Search (EARS 2018). In Proceedings of The 41st International ACM SIGIR Conference on Research and Development in Information Retrieval (SIGIR 18). 2018.

@@

@@

@@

\bibitem{Zhang2015Sentires}  Zhang Y, Zhang M, Liu Y, et al. Boost Phrase-level Polarity Labelling with Review-level Sentiment Classification[J]. Computer Science, 2015.
    Zhang Y, Lai G, Zhang M, et al. Explicit factor models for explainable recommendation based on phrase-level sentiment analysis[C]// International Acm Sigir Conference on Research \& Development in Information Retrieval. ACM, 2014:83-92.

\bibitem{Costa2017LSTM} Costa F, Ouyang S, Dolog P, et al. Automatic Generation of Natural Language Explanations[J]. 2017
\bibitem{Preece2018ExplainAI}Preece A. Asking 'Why' inAI: Explainability of intelligent systems - perspectivesand challenges. Intell Sys Acc Fin Mgmt. 2018;25:63-72.
    %explain AI
\bibitem{Korpan2017navigation}Korpan, R., Epstein, S.L., Aroor, A., Dekel, G.: WHY: Natural explanations from a robot navigator. In: AAAI 2017 Fall Symposium on Natural Communication for Human-Robot Collaboration.
\bibitem{Jose2018cognitive}Jose M. Alonso, Corrado Mencar. Building Cognitive Cities with Explainable Artificial Intelligent Systems. In Proceedings of the First International Workshop on Comprehensibility and Explanation in AI \& ML, 2017.
\bibitem{Lu2011Label}Lu Y, Castellanos M, Dayal U, et al. Automatic construction of a context-aware sentiment lexicon:an optimization approach[C]// International Conference on World Wide Web, WWW 2011, Hyderabad, India, March 28 - April. DBLP, 2011:347-356.
\bibitem{Zhang2017Model}Zhang X , Zhao J , Lui J C S . Modeling the Assimilation-Contrast Effects in Online Product Rating Systems: Debiasing and Recommendations[C]// Eleventh Acm Conference on Recommender Systems. ACM, 2017.
\bibitem{Mimno2012DMR}Mimno D, Mccallum A. Topic Models Conditioned on Arbitrary Features with Dirichlet-multinomial Regression[J]. University of Massachusetts - Amherst, 2012, 2008:411--418.
\end{thebibliography}
\end{document}
